---
title: "Fox to Fracture Article Code"
author: "Anonymous"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

**AI Use Statement**: I used ChatGPT for help in de-bugging some elements of my code, particularly for the mediation analysis. I also used it for assistance in refining certain formatting aspects of the plots.

**Loading in the packages**

```{r}

library(tidyverse)
library(haven)
library(dplyr)
library(psych)
library(corrplot)
library(pscl)
library(car)
library(broom)
library(stargazer)
library(ggeffects)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(htmltools)
library(modelsummary)
library(ggplot2)
library(gt)
library(extrafont)  
library(scales)
library(ggforce)
library(skimr)
```

**Reading in the data files**

```{r}

atp79 <- read_sav("ATP W79.sav")
atp80 <- read_sav("ATP W80.sav")

common_ids <- intersect(atp79$QKEY, atp80$QKEY)

# Number of respondents who appear in both: 5175
length(common_ids)

# Merging into one dataset
atpfinal <- merge(atp79, atp80, by = "QKEY", all = FALSE, suffixes = c("_w79", "_w80"))


```

**Selecting and cleaning variables**

```{r}

# Dropping unnecessary values
atp <- atpfinal %>%  
mutate(
    CAMP20NEWS2_a_W79 = case_when(
      CAMP20NEWS2_a_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_a_W79
    ),
    CAMP20NEWS2_b_W79 = case_when(
      CAMP20NEWS2_b_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_b_W79
    ),
    CAMP20NEWS2_c_W79 = case_when(
      CAMP20NEWS2_c_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_c_W79
    ),
    CAMP20NEWS2_d_W79 = case_when(
      CAMP20NEWS2_d_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_d_W79
    ),
    CAMP20NEWS2_e_W79 = case_when(
      CAMP20NEWS2_e_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_e_W79
    ),
    CAMP20NEWS2_f_W79 = case_when(
      CAMP20NEWS2_f_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_f_W79
    ),
    CAMP20NEWS2_g_W79 = case_when(
      CAMP20NEWS2_g_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_g_W79
    ),
    CAMP20NEWS2_h_W79 = case_when(
      CAMP20NEWS2_h_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_h_W79
    ),
    F_AGECAT_w80 = case_when(
      F_AGECAT_w80 == 99 ~ NA_integer_,
      TRUE ~ F_AGECAT_w80
    ),
    F_GENDER_w80 = case_when(
  F_GENDER_w80 %in% c(3, 99) ~ NA_integer_,
  TRUE ~ F_GENDER_w80
    ),
    F_INC_SDT1_w80 = case_when(
      F_INC_SDT1_w80 == 99 ~ NA_integer_,
      TRUE ~ F_INC_SDT1_w80
    ),
    F_EDUCCAT2_w80 = case_when(
      F_EDUCCAT2_w80 == 99 ~ NA_integer_,
      TRUE ~ F_EDUCCAT2_w80
    ),
    F_IDEO_w80 = case_when(
      F_IDEO_w80 == 99 ~ NA_integer_,
      TRUE ~ F_IDEO_w80
    ),
    F_PARTYSUM_FINAL_w80 = case_when(
      F_PARTYSUM_FINAL_w80 == 9 ~ NA_integer_,
      TRUE ~ F_PARTYSUM_FINAL_w80
    ),
    JAN6HEARD_W80 = case_when(
      JAN6HEARD_W80 == 99 ~ NA_integer_,
      TRUE ~ JAN6HEARD_W80
    ),
    JAN6_DTRESP_W80 = case_when(
      JAN6_DTRESP_W80 == 99 ~ NA_integer_,
      TRUE ~ JAN6_DTRESP_W80
    ),
    TRUMPFUT_W80 = case_when(
      TRUMPFUT_W80 == 99 ~ NA_integer_,
      TRUE ~ TRUMPFUT_W80
    )
  )

# Recoding and reordering variables
atp <- atp %>%  
mutate(
    F_GENDER_w80 = case_when(
      F_GENDER_w80 == 1 ~ 0,
      F_GENDER_w80 == 2 ~ 1,
      TRUE ~ NA_integer_
    ),
    F_IDEO_w80 = case_when( 
    F_IDEO_w80 == 1 ~ 5,
    F_IDEO_w80 == 2 ~ 4,
    F_IDEO_w80 == 3 ~ 3,
    F_IDEO_w80 == 4 ~ 2,
    F_IDEO_w80 == 5 ~ 1
    ),
    JAN6HEARD_W80 = case_when( 
    JAN6HEARD_W80 == 1 ~ 3,
    JAN6HEARD_W80 == 2 ~ 2,
    JAN6HEARD_W80 == 3 ~ 1
    ),
    JAN6_DTRESP_W80 = case_when( 
    JAN6_DTRESP_W80 == 1 ~ 3,
    JAN6_DTRESP_W80 == 2 ~ 2,
    JAN6_DTRESP_W80 == 3 ~ 1
    ),
    TRUMPFUT_W80 = case_when(
      TRUMPFUT_W80 == 1 ~ 1,
      TRUMPFUT_W80 == 2 ~ 0,
      TRUE ~ NA_integer_
    )
  )

## Media variables

media_vars <- c("CAMP20NEWS2_a_W79", "CAMP20NEWS2_b_W79", "CAMP20NEWS2_c_W79",
                "CAMP20NEWS2_d_W79", "CAMP20NEWS2_e_W79", "CAMP20NEWS2_f_W79",
                "CAMP20NEWS2_g_W79", "CAMP20NEWS2_h_W79")

# Recoding each to binary: 1 = uses, 0 = does not use
atp <- atp %>%
  mutate(across(all_of(media_vars),
                ~ ifelse(. %in% c(1, 2), 1,
                         ifelse(. == 3, 0, NA)),
                .names = "use_{col}"))

atp <- atp %>%
  mutate(
    total_sources = rowSums(select(., starts_with("use_")), na.rm = TRUE)
  )

# Dropping respondents with no news sources consulted
atp <- atp %>% filter(total_sources > 0)

table(atp$total_sources)

# Filtering for only Republicans / Lean Republican
atp_rep <- atp %>% filter(F_PARTYSUM_FINAL_w80 == 1)

```

**Updating the media categories**

```{r}

# Creating variables for mainstream conservative media (use_fox) and fringe/talk radio (use_talk)
atp_rep_2 <- atp_rep %>%
  mutate(
    use_fox = ifelse(CAMP20NEWS2_a_W79 %in% c(1, 2), 1, 0),
    use_talk = ifelse(CAMP20NEWS2_h_W79 %in% c(1, 2), 1, 0)
  )

# Creating groups for the media variables
atp_rep_2 <- atp_rep_2 %>%
  mutate(
    cons_media_type = case_when(
      use_fox == 1 & use_talk == 0 ~ "Mainstream_Conservative",
      use_fox == 0 & use_talk == 1 ~ "Fringe_Conservative",
      use_fox == 1 & use_talk == 1 ~ "Both",
      use_fox == 0 & use_talk == 0 ~ "Neither"
    )
  )

atp_rep_2$cons_media_type <- factor(
  atp_rep_2$cons_media_type,
  levels = c("Mainstream_Conservative", "Fringe_Conservative", "Both", "Neither")
)

table(atp_rep_2$cons_media_type)
prop.table(table(atp_rep_2$cons_media_type))


# Labels
pretty_names <- c(
  "(Intercept)" = "Intercept",
  "cons_media_typeFringe_Conservative" = "Fringe Media",
  "cons_media_typeBoth" = "Fringe + Conservative Media",
  "cons_media_typeNeither" = "Neither Media",
  "F_IDEO_w80" = "Ideology",
  "JAN6HEARD_W80" = "Exposure to Jan 6 Information",
  "JAN6_DTRESP_W80" = "Responsibility Attributed",
  "F_GENDER_w80" = "Gender",
  "F_AGECAT_w80" = "Age",
  "F_EDUCCAT2_w80" = "Education",
  "F_INC_SDT1_w80" = "Income"
)

```

**Mediation Analysis**

```{r}

library(mediation)

# Keep only non-missing cases on key variables
atp_rep_3 <- atp_rep_2 %>%
  filter(
    !is.na(cons_media_type),
    !is.na(JAN6_DTRESP_W80),
    !is.na(TRUMPFUT_W80),
    !is.na(F_IDEO_w80),
    !is.na(F_GENDER_w80),
    !is.na(F_AGECAT_w80),
    !is.na(F_EDUCCAT2_w80),
    !is.na(F_INC_SDT1_w80)
  ) 

atp_rep_3$resp_binary <- ifelse(atp_rep_3$JAN6_DTRESP_W80 %in% c(2, 3), 1, 0)
table(atp_rep_3$resp_binary)


# Model 1: Media exposure > Responsibility

m1 <- glm(
  resp_binary ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)

summary(m1) 

# Model 2: Responsibility > Trump support

m2 <- glm(
  TRUMPFUT_W80 ~ resp_binary + cons_media_type + F_IDEO_w80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)

summary(m2) 

# Some diagnostics
vif(m2)
vif(m1)

AIC(m1)
AIC(m2)

BIC(m1)
BIC(m2)


# Mediation Analysis

med_out <- mediate(
  model.m = m1,
  model.y = m2,
  treat   = "cons_media_type",
  mediator = "resp_binary",
  sims = 1000,         
  boot = TRUE
)

summary(med_out)

# Creating tables
coef_labels <- c(
  "cons_media_typeFringe_Conservative" = "Fringe Media",
  "cons_media_typeBoth"                = "Fringe + Conservative Media",
  "cons_media_typeNeither"             = "Neither Media",
  "resp_binary"                        = "Responsibility Attributed",
  "F_IDEO_w80"                         = "Ideology",
  "JAN6HEARD_W80"                      = "Jan 6 Information Exposure",
  "F_GENDER_w80"                       = "Gender",
  "F_AGECAT_w80"                       = "Age",
  "F_EDUCCAT2_w80"                     = "Education",
  "F_INC_SDT1_w80"                     = "Income",
  "(Intercept)"                        = "Intercept"
)

# OR Table
modelsummary(
  list("Mediator Model (m1)" = m1,
       "Outcome Model (m2)"   = m2),
  exponentiate = TRUE,
  coef_map = coef_labels,               
  statistic    = "({p.value})",
  fmt          = 3,
  stars        = TRUE,
  title        = "Odds-Ratios for Mediator & Outcome Models"
) 

# Percentages
100*(exp(m1$coefficients[-1])-1)
100*(exp(m2$coefficients[-1])-1)

# Log odds Table
modelsummary(
  list("Mediator Model (m1)" = m1,
       "Outcome Model (m2)"   = m2),
  exponentiate = FALSE,
  coef_map = coef_labels,               
  statistic    = "({p.value})",
  fmt          = 3,
  stars        = TRUE,
  title        = "Log-Odds for Mediator & Outcome Models"
) 

```

**Share of Correctly-predicted responses and McFadden R2**

```{r}

m1_1 <- glm(
  resp_binary ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  family = binomial(link = "logit")
)

pR2(m1_1)["McFadden"]

m2_2 <- glm(
  TRUMPFUT_W80 ~ resp_binary + cons_media_type + F_IDEO_w80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  family = binomial(link = "logit")
)
pR2(m2_2)["McFadden"]


# Share of correctly predicted responses

# Mediator model (m1)
# Predict probabilities
probs_m1 <- predict(m1, newdata = atp_rep_3, type = "response")

# Convert to predicted binary values (0/1)
pred_m1 <- ifelse(probs_m1 >= 0.5, 1, 0)

# Tabulate predictions vs actual
tab_m1 <- table(Predicted = pred_m1, Actual = atp_rep_3$resp_binary)
tab_m1

# Calculate proportion of correctly predicted
accuracy_m1 <- sum(diag(tab_m1)) / sum(tab_m1)
accuracy_m1


# Outcome model (m2)
# Predict probabilities
probs_m2 <- predict(m2, newdata = atp_rep_3, type = "response")

# Convert to predicted binary values
pred_m2 <- ifelse(probs_m2 >= 0.5, 1, 0)

# Tabulate predictions vs actual
tab_m2 <- table(Predicted = pred_m2, Actual = atp_rep_3$TRUMPFUT_W80)
tab_m2

# Calculate overall accuracy
accuracy_m2 <- sum(diag(tab_m2)) / sum(tab_m2)
accuracy_m2

```

**Separate OR tables for each model**

```{r}

# Model 1
ORs_m1 <- exp(cbind(OR = coef(m1), confint(m1)))
ORs_m1

OR_table1 <- kable(round(ORs_m1, 3), format = "html", caption = "Odds Ratios and 95% CI - Mediator Model")

save_html(HTML(as.character(OR_table1)), file = "OddsRatiosM1Final.html")

# Model 2
ORs_m2 <- exp(cbind(OR = coef(m2), confint(m2)))
ORs_m2

OR_table2 <- kable(round(ORs_m2, 3), format = "html", caption = "Odds Ratios and 95% CI - Outcome Model")

save_html(HTML(as.character(OR_table2)), file = "OddsRatiosM2Final.html")


```

**Odds-Ratio Plots**

```{r}

# Mediator model (m1)

tidy_m1 <- broom::tidy(m1, conf.int = TRUE, exponentiate = TRUE) %>%
filter(term != "(Intercept)") %>%
mutate(significant = ifelse(p.value < 0.05, "Yes", "No"))

# Outcome model (m2)

tidy_m2 <- broom::tidy(m2, conf.int = TRUE, exponentiate = TRUE) %>%
filter(term != "(Intercept)") %>%
mutate(significant = ifelse(p.value < 0.05, "Yes", "No"))

# Plot for m1 (Mediator)

plot_m1 <- ggplot(tidy_m1, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8) +
  scale_color_manual(values = c("Yes" = "#1f77b4", "No" = "#7f7f7f")) +
  coord_flip() +
  scale_x_discrete(labels = c(
    "cons_media_typeFringe_Conservative" = "Fringe Media",
    "cons_media_typeBoth" = "Fringe + Mainstream Conservative Media",
    "cons_media_typeNeither" = "Neither Media",
    "F_IDEO_w80" = "Ideology",
    "JAN6HEARD_W80" = "Jan 6 Information Exposure",
    "F_EDUCCAT2_w80" = "Education",
    "F_INC_SDT1_w80" = "Income",
    "F_AGECAT_w80" = "Age",
    "F_GENDER_w80" = "Gender")) +
  labs(
    x = "Predictor",
    y = "Odds Ratio",
    color = "Significant",
    title = "Mediator Model (m1): Odds Ratios with 95% CI"
  ) +
  theme_minimal(base_family = "Helvetica") +  # Set font
  theme(
    plot.background = element_rect(fill = "#ffffff", color = NA),  # light gray background
    panel.background = element_rect(fill = "#DEDFDF", color = NA),   # panel white
    panel.grid.major = element_line(color = "#ffffff"),             # gray grid lines
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 12, color = "#333333"),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

plot_m1



# Plot for m2 (Outcome)


plot_m2 <- ggplot(tidy_m2, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8) +
  scale_color_manual(values = c("Yes" = "#d62728", "No" = "#7f7f7f")) +  # red for significant
  coord_flip() +
  scale_x_discrete(labels = c(
    "resp_binary" = "Responsibility Attributed to Trump",
    "cons_media_typeFringe_Conservative" = "Fringe Media",
    "cons_media_typeBoth" = "Fringe + Mainstream Conservative Media",
    "cons_media_typeNeither" = "Neither Media",
    "F_IDEO_w80" = "Ideology",
    "F_EDUCCAT2_w80" = "Education",
    "F_INC_SDT1_w80" = "Income",
    "F_AGECAT_w80" = "Age",
    "F_GENDER_w80" = "Gender"
  )) +
  labs(
    x = "Predictor",
    y = "Odds Ratio",
    color = "Significant",
    title = "Outcome Model (m2): Odds Ratios with 95% CI"
  ) +
  theme_minimal(base_family = "Helvetica") +
  theme(
    plot.background = element_rect(fill = "#ffffff", color = NA),
    panel.background = element_rect(fill = "#DEDFDF", color = NA),
    panel.grid.major = element_line(color = "#ffffff"),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 12, color = "#333333"),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

plot_m2


```

**Predicted Probabilities**

```{r}

# Predicted probabilities for m1 (Mediator)
# Predict probability of assigning responsibility (resp_binary)

atp_rep_3$pred_prob_m1 <- predict(m1, newdata = atp_rep_3, type = "response")

# Mean predicted probability by media type

atp_rep_3 %>%
group_by(cons_media_type) %>%
summarise(mean_pred_prob = mean(pred_prob_m1, na.rm = TRUE))


# Predicted probabilities for m2 (Outcome)
# Predict probability of supporting Trump (TRUMPFUT_W80)

atp_rep_3$pred_prob_m2 <- predict(m2, newdata = atp_rep_3, type = "response")

# Mean predicted probability by responsibility (resp_binary)

atp_rep_3 %>%
group_by(resp_binary) %>%
summarise(mean_pred_prob = mean(pred_prob_m2, na.rm = TRUE))
```

**Predicted Probability Plots**

```{r}

# Compute predicted probabilities for m1
pred_m1 <- ggpredict(m1, terms = "cons_media_type")

# Predicted probability plot for m1

ggplot(pred_m1, aes(x = x, y = predicted)) +
geom_point(size = 4, color = "#1f77b4") +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8, color = "#1f77b4") +
scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
scale_x_discrete(labels = c(
"Fringe_Conservative" = "Fringe",
"Both" = "Fringe + Conservative",
"Neither" = "Neither",
"Mainstream_Conservative" = "Conservative"
)) +
labs(
x = "Media Consumption Type",
y = "Predicted Probability of Attributing Responsibility",
title = "Predicted Probability of Attributing Responsibility by Media Type"
) +
coord_flip() +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
)


# Compute predicted probabilities of supporting Trump by responsibility (m2)
pred_resp <- ggpredict(m2, terms = "resp_binary")


# Predicted probability plot for m2

ggplot(pred_resp, aes(x = x, y = predicted)) +
geom_point(size = 4, color = "#d62728") +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8, color = "#d62728") +
scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
scale_x_continuous(
breaks = c(0, 1),
labels = c("Low Responsibility", "High Responsibility")
) +
labs(
x = "Responsibility Attributed to Trump",
y = "Predicted Probability of Supporting Trump",
title = "Predicted Probability of Supporting Trump by Responsibility Attribution"
) +
coord_flip() +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
legend.position = "none"
)


```

**Mediation Analysis Plots**

```{r}

# Prepare mediation effects
med_effects <- data.frame(
  Effect = c("Indirect (ACME)", "Direct (ADE)", "Total Effect"),
  Estimate = c(med_out$d0, med_out$z0, med_out$tau.coef),
  Lower = c(med_out$d0.ci[1], med_out$z0.ci[1], med_out$tau.ci[1]),
  Upper = c(med_out$d0.ci[2], med_out$z0.ci[2], med_out$tau.ci[2])
)

# Adjusted mediation effects plot

ggplot(med_effects, aes(x = Effect, y = Estimate)) +
geom_point(size = 4, color = "#4FB663") +
geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, size = 0.8, color = "#4FB663") +
geom_hline(yintercept = 0, linetype = "dashed", color = "#7f7f7f") +
coord_flip() +
labs(
x = "",
y = "Effect Estimate",
title = "Mediation Analysis: Direct, Indirect, and Total Effects"
) +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
legend.position = "none"
)


```

**Descriptive Statistics**

```{r}

# Descriptive Statistics

vars <- c("resp_binary", "cons_media_type", "F_IDEO_w80", "F_GENDER_w80", "F_AGECAT_w80", "F_EDUCCAT2_w80", "F_INC_SDT1_w80", "JAN6HEARD_W80", "F_PARTYSUM_FINAL_w80")
skim_out <- skim(atp_rep_3[vars])

# Create HTML table
html_table <- kable(skim_out, format = "html") %>%
  kable_styling()

# Save to HTML file
save_kable(html_table, "skim_descriptives.html")

desc <- describe(atp_rep_3[vars])

# Convert describe() output to HTML manually
html <- paste0(
  "<html><body><h2>Descriptive Statistics</h2>",
  "<table border='1' cellpadding='5'>",
  "<tr><th>", paste(colnames(desc), collapse="</th><th>"), "</th></tr>",
  paste(
    apply(desc, 1, function(row)
      paste0("<tr><td>", paste(row, collapse="</td><td>"), "</td></tr>")
    ),
    collapse=""
  ),
  "</table></body></html>"
)

writeLines(html, "descriptive_stats.html")

```
