---
title: "Republican Media Diets - Intraparty Realignment"
author: N/A
format: pdf
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}

library(tidyverse)
library(haven)
library(dplyr)
library(psych)
library(corrplot)
library(pscl)
library(car)
library(broom)
library(stargazer)
library(ggeffects)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(htmltools)
library(modelsummary)

```

**Note:** I apologize in advance for the messiness of this code! Please do not hesitate to ask if you need clarification.

**AI Use Statement**: I used ChatGPT for help in de-bugging certain elements of the code, particularly for the mediation analysis. I also used it for assistance in the formatting aspects of my plots.

------------------------------------------------------------------------

Reading in the data files and merging into one

```{r}

atp79 <- read_sav("ATP W79.sav")
atp80 <- read_sav("ATP W80.sav")


# Number of respondents who appear in both: 5175
common_ids <- intersect(atp79$QKEY, atp80$QKEY)
length(common_ids)

# Merge into one dataset, add suffixes to differentiate between
atpfinal <- merge(atp79, atp80, by = "QKEY", all = FALSE, suffixes = c("_w79", "_w80"))

```

Selecting the variables

```{r}

names(atp80)

atp80$TRUMPFUT_W80

# Dropping unneeded values

atp <- atpfinal %>%  
mutate(
    # Recode 'CAMP20NEWS2_a_W79' to drop value 99
    CAMP20NEWS2_a_W79 = case_when(
      CAMP20NEWS2_a_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_a_W79
    ),
    # Recode 'CAMP20NEWS2_b_W79' to drop value 99
    CAMP20NEWS2_b_W79 = case_when(
      CAMP20NEWS2_b_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_b_W79
    ),
    # Recode 'CAMP20NEWS2_c_W79' to drop value 99
    CAMP20NEWS2_c_W79 = case_when(
      CAMP20NEWS2_c_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_c_W79
    ),
    # Recode 'CAMP20NEWS2_d_W79' to drop value 99
    CAMP20NEWS2_d_W79 = case_when(
      CAMP20NEWS2_d_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_d_W79
    ),
    # Recode 'CAMP20NEWS2_e_W79' to drop value 99
    CAMP20NEWS2_e_W79 = case_when(
      CAMP20NEWS2_e_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_e_W79
    ),
    # Recode 'CAMP20NEWS2_f_W79' to drop value 99
    CAMP20NEWS2_f_W79 = case_when(
      CAMP20NEWS2_f_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_f_W79
    ),
    # Recode 'CAMP20NEWS2_g_W79' to drop value 99
    CAMP20NEWS2_g_W79 = case_when(
      CAMP20NEWS2_g_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_g_W79
    ),
    # Recode 'CAMP20NEWS2_h_W79' to drop value 99
    CAMP20NEWS2_h_W79 = case_when(
      CAMP20NEWS2_h_W79 == 99 ~ NA_integer_,
      TRUE ~ CAMP20NEWS2_h_W79
    ),
    # Recode 'F_AGECAT_w80' to drop values 99
    F_AGECAT_w80 = case_when(
      F_AGECAT_w80 == 99 ~ NA_integer_,
      TRUE ~ F_AGECAT_w80
    ),
    # Recode 'F_GENDER_w80' to drop values 3 and 99
    F_GENDER_w80 = case_when(
  F_GENDER_w80 %in% c(3, 99) ~ NA_integer_,
  TRUE ~ F_GENDER_w80
    ),
    # Recode 'F_INC_SDT1_w80' to drop values 99
    F_INC_SDT1_w80 = case_when(
      F_INC_SDT1_w80 == 99 ~ NA_integer_,
      TRUE ~ F_INC_SDT1_w80
    ),
    # Recode 'F_EDUCCAT2_w80' to drop values 99
    F_EDUCCAT2_w80 = case_when(
      F_EDUCCAT2_w80 == 99 ~ NA_integer_,
      TRUE ~ F_EDUCCAT2_w80
    ),
    # Recode 'F_IDEO_w80' to drop values 99
    F_IDEO_w80 = case_when(
      F_IDEO_w80 == 99 ~ NA_integer_,
      TRUE ~ F_IDEO_w80
    ),
    # Recode 'F_PARTYSUM_FINAL_w80' to drop values 9
    F_PARTYSUM_FINAL_w80 = case_when(
      F_PARTYSUM_FINAL_w80 == 9 ~ NA_integer_,
      TRUE ~ F_PARTYSUM_FINAL_w80
    ),
    # Recode 'JAN6HEARD_W80' to drop values 99
    JAN6HEARD_W80 = case_when(
      JAN6HEARD_W80 == 99 ~ NA_integer_,
      TRUE ~ JAN6HEARD_W80
    ),
  # Recode 'JAN6_DTRESP_W80' to drop values 99
    JAN6_DTRESP_W80 = case_when(
      JAN6_DTRESP_W80 == 99 ~ NA_integer_,
      TRUE ~ JAN6_DTRESP_W80
    ),
  # Recode 'TRUMPFUT_W80' to drop values 99
    TRUMPFUT_W80 = case_when(
      TRUMPFUT_W80 == 99 ~ NA_integer_,
      TRUE ~ TRUMPFUT_W80
    )
  )

# Recoding and reordering variables

atpfinal$JAN6_DTRESP_W80

atp <- atp %>%  
mutate(
    # Recoding F_GENDER_w80 1/2 into 0/1 
    F_GENDER_w80 = case_when(
      F_GENDER_w80 == 1 ~ 0,
      F_GENDER_w80 == 2 ~ 1,
      TRUE ~ NA_integer_
    ),
    # Re-ordering 'F_IDEO_w80' into ascending by movement towards the right
    F_IDEO_w80 = case_when( 
    F_IDEO_w80 == 1 ~ 5,
    F_IDEO_w80 == 2 ~ 4,
    F_IDEO_w80 == 3 ~ 3,
    F_IDEO_w80 == 4 ~ 2,
    F_IDEO_w80 == 5 ~ 1
    ),
    # Re-ordering 'JAN6HEARD_W80' into ascending by amount of exposure
    JAN6HEARD_W80 = case_when( 
    JAN6HEARD_W80 == 1 ~ 3,
    JAN6HEARD_W80 == 2 ~ 2,
    JAN6HEARD_W80 == 3 ~ 1
    ),
    # Re-ordering 'JAN6_DTRESP_W80' into ascending by amount of responsibility
    JAN6_DTRESP_W80 = case_when( 
    JAN6_DTRESP_W80 == 1 ~ 3,
    JAN6_DTRESP_W80 == 2 ~ 2,
    JAN6_DTRESP_W80 == 3 ~ 1
    ),
    # Recoding TRUMPFUT_W80 1/2 into 0/1 
    TRUMPFUT_W80 = case_when(
      TRUMPFUT_W80 == 1 ~ 1,
      TRUMPFUT_W80 == 2 ~ 0,
      TRUE ~ NA_integer_
    )
  )

## Finally treating media variables

media_vars <- c("CAMP20NEWS2_a_W79", "CAMP20NEWS2_b_W79", "CAMP20NEWS2_c_W79",
                "CAMP20NEWS2_d_W79", "CAMP20NEWS2_e_W79", "CAMP20NEWS2_f_W79",
                "CAMP20NEWS2_g_W79", "CAMP20NEWS2_h_W79")

# Recode each to binary: 1 = uses (major/minor), 0 = does not use
atp <- atp %>%
  mutate(across(all_of(media_vars),
                ~ ifelse(. %in% c(1, 2), 1,
                         ifelse(. == 3, 0, NA)),
                .names = "use_{col}"))


atp <- atp %>%
  mutate(
    total_sources = rowSums(select(., starts_with("use_")), na.rm = TRUE)
  )

# Drop respondents with no sources
atp <- atp %>% filter(total_sources > 0)

table(atp$total_sources)


# Filtering for only Republicans
atp_rep <- atp %>% filter(F_PARTYSUM_FINAL_w80 == 1)

```

Updating media categories

```{r}

atp_rep_2 <- atp_rep %>%
  mutate(
    use_fox = ifelse(CAMP20NEWS2_a_W79 %in% c(1, 2), 1, 0),
    use_talk = ifelse(CAMP20NEWS2_h_W79 %in% c(1, 2), 1, 0)
  )

# Creating groups for the media variables

atp_rep_2 <- atp_rep_2 %>%
  mutate(
    cons_media_type = case_when(
      use_fox == 1 & use_talk == 0 ~ "Mainstream_Conservative",
      use_fox == 0 & use_talk == 1 ~ "Fringe_Conservative",
      use_fox == 1 & use_talk == 1 ~ "Both",
      use_fox == 0 & use_talk == 0 ~ "Neither"
    )
  )

atp_rep_2$cons_media_type <- factor(
  atp_rep_2$cons_media_type,
  levels = c("Mainstream_Conservative", "Fringe_Conservative", "Both", "Neither")
)

table(atp_rep_2$cons_media_type)
prop.table(table(atp_rep_2$cons_media_type))

# Model Without Mediation Analysis
testingagain_2 <- glm(
  TRUMPFUT_W80 ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 +
    JAN6_DTRESP_W80 + F_GENDER_w80 + F_AGECAT_w80 +
    F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_2,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)
summary(testingagain_2)

### Use for step 1 of mediation to prove Baron and Kenny's steps
testingagain_3 <- glm(
  TRUMPFUT_W80 ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 + F_GENDER_w80 + F_AGECAT_w80 +
    F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_2,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)
summary(testingagain_3)

modelsummary(
  testingagain_3,
  coef_map = pretty_names,
  exponentiate = FALSE,
  #coef_map = coef_labels,               # pretty names
  statistic    = "({p.value})",
  fmt          = 3,
  stars        = TRUE,
  title        = "Log Odds for Step 1 Model"
)


pretty_names <- c(
  "(Intercept)" = "Intercept",
  "cons_media_typeFringe_Conservative" = "Fringe Media",
  "cons_media_typeBoth" = "Fringe + Conservative Media",
  "cons_media_typeNeither" = "Neither Media",
  "F_IDEO_w80" = "Ideology",
  "JAN6HEARD_W80" = "Exposure to Jan 6 Information",
  "JAN6_DTRESP_W80" = "Responsibility Attributed",
  "F_GENDER_w80" = "Gender",
  "F_AGECAT_w80" = "Age",
  "F_EDUCCAT2_w80" = "Education",
  "F_INC_SDT1_w80" = "Income"
)

modelsummary(
  testingagain_2,
  coef_map = pretty_names,
  #estimate = "{estimate} ({conf.low}, {conf.high})",  # shows CI
  stars = TRUE,
  title = "Log-Odds Coefficients from Single-Stage Model"
)


library(pscl)
pR2(testingagain_2)["McFadden"]

# Share of correctly predicted responses

probs <-predict(object = testingagain_2, newdata=atp_rep_2, type="response")
atp_rep_2 <-cbind(atp_rep_2, probs) 
atp_rep_2$pred_support<-0    
atp_rep_2$pred_support[atp_rep_2$probs>=0.5]<-1  

accuracy <- table(atp_rep_2$pred_support, atp_rep_2$TRUMPFUT_W80)  
accuracy

prop <-prop.table(accuracy)  
prop 


corr_pred<-prop[1,1]+prop[2,2] 
corr_pred

# Odds-ratio

ORs_final <- exp(cbind(OR = coef(testingagain_2), confint(testingagain_2)))
ORs_final

OR_table <- kable(round(ORs_final, 3), format = "html", caption = "Odds Ratios and 95% CI")

save_html(HTML(as.character(OR_table)), file = "OddsRatios.html")


100*(exp(testingagain_2$coefficients[-1])-1)

stargazer(testingagain_2,
          type = "html",            # Change to "latex" or "html" if needed
          title = "Logistic Regression Results",
          dep.var.labels = "Support Trump in Future",
          covariate.labels = c(
            "Fringe Type Only",
            "Fringe and Mainstream",
            "Neither Media Type",
            "Ideology (Higher = More Conservative)",
            "Exposure to Jan 6 Information",
            "Assigns Trump Responsibility",
            "Gender (1 = Male)",
            "Age",
            "Education",
            "Income"
          ),
          digits = 3,
          no.space = TRUE,
          out = "regression_results.html")

```

Graphing results

```{r}

# Plotting odds-ratios

model_df <- tidy(testingagain_2, conf.int = TRUE) %>%
  mutate(
    odds_ratio = exp(estimate),
    conf.low   = exp(conf.low),
    conf.high  = exp(conf.high)
  )

selected_vars <- c(
  "cons_media_typeBoth", "cons_media_typeNeither", "F_IDEO_w80", "JAN6_DTRESP_W80"
)

model_subset <- model_df %>%
  filter(term %in% selected_vars)

ggplot(model_subset, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  coord_flip() +
  labs(
    title = "Odds Ratios for Trump Future Support",
    x = "Predictor",
    y = "Odds Ratio for Trump Future Support"
  ) +
  theme_minimal()

```

Plotting predicted probabilities

```{r}

# Predicted probability plot using ggpredict

# Install/load packages if needed
# install.packages("ggeffects")
library(ggeffects)
library(ggplot2)

# Generate predicted probabilities for the media variable
pred_media <- ggpredict(testingagain_2, terms = "cons_media_type")

# Plot predicted probabilities with confidence intervals
ggplot(pred_media, aes(x = x, y = predicted)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .15) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    title = "Predicted Probability of Supporting Trump by Conservative Media Diet (Republicans)",
    x = "Conservative Media Diet",
    y = "Predicted Probability"
  ) +
  theme_minimal(base_size = 13)


```

Trying a mediation analysis

```{r}

summary(testingagain_3)

library(mediation)


atp_rep_3 <- atp_rep_2 %>%
  filter(
    !is.na(cons_media_type),
    !is.na(JAN6_DTRESP_W80),
    !is.na(TRUMPFUT_W80),
    !is.na(F_IDEO_w80),
    !is.na(F_GENDER_w80),
    !is.na(F_AGECAT_w80),
    !is.na(F_EDUCCAT2_w80),
    !is.na(F_INC_SDT1_w80)
  )

atp_rep_3$resp_binary <- ifelse(atp_rep_3$JAN6_DTRESP_W80 %in% c(2, 3), 1, 0)
table(atp_rep_3$resp_binary)


# Treatment model

m1 <- glm(
  resp_binary ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)

summary(m1)

m2 <- glm(
  TRUMPFUT_W80 ~ resp_binary + cons_media_type + F_IDEO_w80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  weights = WEIGHT_W80,
  family = binomial(link = "logit")
)

summary(m2)
vif(m2)
vif(m1)

AIC(m1)
AIC(m2)

BIC(m1)
BIC(m2)

# mediation analysis

med_out <- mediate(
  model.m = m1,
  model.y = m2,
  treat   = "cons_media_type",
  mediator = "resp_binary",
  sims = 1000,         # bootstrap simulations
  boot = TRUE
)

summary(med_out)


library(gt)

med_df %>%
  gt() %>%
  tab_header(title = "Mediation Analysis Results") %>%
  gtsave("mediation_results.html")


coef_labels <- c(
  "cons_media_typeFringe_Conservative" = "Fringe Media",
  "cons_media_typeBoth"                = "Fringe + Conservative Media",
  "cons_media_typeNeither"             = "Neither Media",
  "resp_binary"                        = "Responsibility Attributed",
  "F_IDEO_w80"                         = "Ideology",
  "JAN6HEARD_W80"                      = "Jan 6 Information Exposure",
  "F_GENDER_w80"                       = "Gender",
  "F_AGECAT_w80"                       = "Age",
  "F_EDUCCAT2_w80"                     = "Education",
  "F_INC_SDT1_w80"                     = "Income",
  "(Intercept)"                        = "Intercept"
)


modelsummary(
  list("Mediator Model (m1)" = m1,
       "Outcome Model (m2)"   = m2),
  exponentiate = TRUE,
  coef_map = coef_labels,               
  statistic    = "({p.value})",
  fmt          = 3,
  stars        = TRUE,
  title        = "Odds-Ratios for Mediator & Outcome Models"
)

# Percentages
100*(exp(m1$coefficients[-1])-1)
100*(exp(m2$coefficients[-1])-1)
100*(exp(testingagain_3$coefficients[-1])-1)


summary(testingagain_3)
summary(m1)
# Side by side table for Log-Odds


modelsummary(
  list("Mediator Model (m1)" = m1,
       "Outcome Model (m2)"   = m2),
  exponentiate = FALSE,
  coef_map = coef_labels,               # pretty names
  statistic    = "({p.value})",
  fmt          = 3,
  stars        = TRUE,
  title        = "Log-Odds for Mediator & Outcome Models"
)

summary(med_out)
plot(med_out, main = "Mediation Analysis: Effects of Media on Trump Support",
     xlab = "Effect Size (ACME or ADE)", ylab = "Density", col = "forestgreen")

summary(model.m)   # gives 'a'


```

Share of correctly predicted responses and mcfadden

```{r}

m1_1 <- glm(
  resp_binary ~ cons_media_type + F_IDEO_w80 + JAN6HEARD_W80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  family = binomial(link = "logit")
)

library(pscl)
pR2(m1_1)["McFadden"]

m2_2 <- glm(
  TRUMPFUT_W80 ~ resp_binary + cons_media_type + F_IDEO_w80 +
    F_GENDER_w80 + F_AGECAT_w80 + F_EDUCCAT2_w80 + F_INC_SDT1_w80,
  data = atp_rep_3,
  family = binomial(link = "logit")
)
pR2(m2_2)["McFadden"]


# Share of correctly predicted responses

# ----------------------------
# Step 1: Mediator model (m1)
# ----------------------------
# Predict probabilities
probs_m1 <- predict(m1, newdata = atp_rep_3, type = "response")

# Convert to predicted binary values (0/1)
pred_m1 <- ifelse(probs_m1 >= 0.5, 1, 0)

# Tabulate predictions vs actual
tab_m1 <- table(Predicted = pred_m1, Actual = atp_rep_3$resp_binary)
tab_m1

# Calculate proportion of correctly predicted
accuracy_m1 <- sum(diag(tab_m1)) / sum(tab_m1)
accuracy_m1

# ----------------------------
# Step 2: Outcome model (m2)
# ----------------------------
# Predict probabilities
probs_m2 <- predict(m2, newdata = atp_rep_3, type = "response")

# Convert to predicted binary values
pred_m2 <- ifelse(probs_m2 >= 0.5, 1, 0)

# Tabulate predictions vs actual
tab_m2 <- table(Predicted = pred_m2, Actual = atp_rep_3$TRUMPFUT_W80)
tab_m2

# Calculate overall accuracy
accuracy_m2 <- sum(diag(tab_m2)) / sum(tab_m2)
accuracy_m2

```

Odds Ratios for each model

```{r}

library(broom)
library(dplyr)
library(knitr)
library(kableExtra)

# Model 1
ORs_m1 <- exp(cbind(OR = coef(m1), confint(m1)))
ORs_m1

OR_table1 <- kable(round(ORs_m1, 3), format = "html", caption = "Odds Ratios and 95% CI - Mediator Model")

save_html(HTML(as.character(OR_table1)), file = "OddsRatiosM1Final.html")

# Model 2
ORs_m2 <- exp(cbind(OR = coef(m2), confint(m2)))
ORs_m2

OR_table2 <- kable(round(ORs_m2, 3), format = "html", caption = "Odds Ratios and 95% CI - Outcome Model")

save_html(HTML(as.character(OR_table2)), file = "OddsRatiosM2Final.html")


```

Odds-Ratio Plots

```{r}

library(broom)
library(dplyr)
library(ggplot2)

# Mediator model (m1)

tidy_m1 <- broom::tidy(m1, conf.int = TRUE, exponentiate = TRUE) %>%
filter(term != "(Intercept)") %>%
mutate(significant = ifelse(p.value < 0.05, "Yes", "No"))

# Outcome model (m2)

tidy_m2 <- broom::tidy(m2, conf.int = TRUE, exponentiate = TRUE) %>%
filter(term != "(Intercept)") %>%
mutate(significant = ifelse(p.value < 0.05, "Yes", "No"))
-

# Plot for m1 (Mediator)

plot_m1 <- ggplot(tidy_m1, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
geom_point(size = 3) +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
scale_color_manual(values = c("Yes" = "steelblue", "No" = "grey50")) +
coord_flip() +
labs(
x = "Predictor",
y = "Odds Ratio",
color = "Significant",
title = "Mediator Model (m1): Odds Ratios with 95% CI"
) +
theme_minimal()

plot_m1

library(ggplot2)
library(extrafont)  

plot_m1 <- ggplot(tidy_m1, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8) +
  scale_color_manual(values = c("Yes" = "#1f77b4", "No" = "#7f7f7f")) +
  coord_flip() +
  scale_x_discrete(labels = c(
    "cons_media_typeFringe_Conservative" = "Fringe Media",
    "cons_media_typeBoth" = "Fringe + Mainstream Conservative Media",
    "cons_media_typeNeither" = "Neither Media",
    "F_IDEO_w80" = "Ideology",
    "JAN6HEARD_W80" = "Jan 6 Information Exposure",
    "F_EDUCCAT2_w80" = "Education",
    "F_INC_SDT1_w80" = "Income",
    "F_AGECAT_w80" = "Age",
    "F_GENDER_w80" = "Gender")) +
  labs(
    x = "Predictor",
    y = "Odds Ratio",
    color = "Significant",
    title = "Mediator Model (m1): Odds Ratios with 95% CI"
  ) +
  theme_minimal(base_family = "Helvetica") +  # Set font
  theme(
    plot.background = element_rect(fill = "#ffffff", color = NA),  # light gray background
    panel.background = element_rect(fill = "#DEDFDF", color = NA),   # panel white
    panel.grid.major = element_line(color = "#ffffff"),             # gray grid lines
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 12, color = "#333333"),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

plot_m1


# plot for m2 (Outcome)

plot_m2 <- ggplot(tidy_m2, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
geom_point(size = 3) +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
scale_color_manual(values = c("Yes" = "darkred", "No" = "grey50")) +
coord_flip() +
labs(
x = "Predictor",
y = "Odds Ratio",
color = "Significant",
title = "Outcome Model (m2): Odds Ratios with 95% CI"
) +
theme_minimal()

plot_m2




# Tidy m2 for plotting

tidy_m2 <- broom::tidy(m2, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(significant = ifelse(p.value < 0.05, "Yes", "No"))

# Plot odds ratios for m2

plot_m2 <- ggplot(tidy_m2, aes(x = reorder(term, estimate), y = estimate, color = significant)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8) +
  scale_color_manual(values = c("Yes" = "#d62728", "No" = "#7f7f7f")) +  # red for significant
  coord_flip() +
  scale_x_discrete(labels = c(
    "resp_binary" = "Responsibility Attributed to Trump",
    "cons_media_typeFringe_Conservative" = "Fringe Media",
    "cons_media_typeBoth" = "Fringe + Mainstream Conservative Media",
    "cons_media_typeNeither" = "Neither Media",
    "F_IDEO_w80" = "Ideology",
    "F_EDUCCAT2_w80" = "Education",
    "F_INC_SDT1_w80" = "Income",
    "F_AGECAT_w80" = "Age",
    "F_GENDER_w80" = "Gender"
  )) +
  labs(
    x = "Predictor",
    y = "Odds Ratio",
    color = "Significant",
    title = "Outcome Model (m2): Odds Ratios with 95% CI"
  ) +
  theme_minimal(base_family = "Helvetica") +
  theme(
    plot.background = element_rect(fill = "#ffffff", color = NA),
    panel.background = element_rect(fill = "#DEDFDF", color = NA),
    panel.grid.major = element_line(color = "#ffffff"),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 12, color = "#333333"),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

plot_m2


```

Predicted Probabilities

```{r}

library(dplyr)



# predicted probabilities for m1 (Mediator)

# Predict probability of assigning responsibility (resp_binary)

atp_rep_3$pred_prob_m1 <- predict(m1, newdata = atp_rep_3, type = "response")

atp_rep_3 %>%
group_by(cons_media_type) %>%
summarise(mean_pred_prob = mean(pred_prob_m1, na.rm = TRUE))



# Predicted probabilities for m2 (Outcome)

# Predict probability of supporting Trump (TRUMPFUT_W80)

atp_rep_3$pred_prob_m2 <- predict(m2, newdata = atp_rep_3, type = "response")

# Example: mean predicted probability by responsibility (resp_binary)

atp_rep_3 %>%
group_by(resp_binary) %>%
summarise(mean_pred_prob = mean(pred_prob_m2, na.rm = TRUE))
```

Predicted Probability Plots

```{r}

library(ggeffects)
library(ggplot2)

# predicted probabilities for m1
pred_m1 <- ggpredict(m1, terms = "cons_media_type")

library(scales)

plot_pred_m1 <- ggplot(pred_m1, aes(x = x, y = predicted)) +
  geom_point(size = 4, color = "#1f77b4") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8, color = "#1f77b4") +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0,1)) +
  scale_x_discrete(labels = c(
    "Fringe_Conservative" = "Fringe",
    "Both" = "Fringe + Conservative",
    "Neither" = "Neither",
    "Mainstream_Conservative" = "Conservative"
  )) +
  labs(
    x = "Media Consumption Type",
    y = "Predicted Probability of Attributing Responsibility",
    title = "Predicted Probability of Attributing Responsibility by Media Type"
  ) +
  theme_minimal(base_family = "Helvetica") +
  theme(
    plot.background = element_rect(fill = "#ffffff", color = NA),
    panel.background = element_rect(fill = "#DEDFDF", color = NA),
    panel.grid.major = element_line(color = "#ffffff"),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 12, color = "#333333"),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
  )

plot_pred_m1

# Flipping

library(ggplot2)
library(scales)

# predicted probability plot for m1 with flipped coordinates

ggplot(pred_m1, aes(x = x, y = predicted)) +
geom_point(size = 4, color = "#1f77b4") +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8, color = "#1f77b4") +
scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
scale_x_discrete(labels = c(
"Fringe_Conservative" = "Fringe",
"Both" = "Fringe + Conservative",
"Neither" = "Neither",
"Mainstream_Conservative" = "Conservative"
)) +
labs(
x = "Media Consumption Type",
y = "Predicted Probability of Attributing Responsibility",
title = "Predicted Probability of Attributing Responsibility by Media Type"
) +
coord_flip() +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
)


# Predicted probabilities of supporting Trump by responsibility (m2)
pred_resp <- ggpredict(m2, terms = "resp_binary")

# Plot
ggplot(pred_resp, aes(x = x, y = predicted)) +
  geom_point(size = 3, color = "steelblue") +
  geom_line(group = 1, color = "steelblue") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "steelblue") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = c(0,1), labels = c("Low Responsibility", "High Responsibility")) +
  labs(
    x = "Responsibility Attributed to Trump",
    y = "Predicted Probability of Supporting Trump",
    title = "Predicted Probability of Supporting Trump by Responsibility Attribution"
  ) +
  theme_minimal()

library(ggplot2)
library(scales)

# Adjusted predicted probability plot for m2

ggplot(pred_resp, aes(x = x, y = predicted)) +
geom_point(size = 4, color = "#d62728") +
geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.8, color = "#d62728") +
scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
scale_x_continuous(
breaks = c(0, 1),
labels = c("Low Responsibility", "High Responsibility")
) +
labs(
x = "Responsibility Attributed to Trump",
y = "Predicted Probability of Supporting Trump",
title = "Predicted Probability of Supporting Trump by Responsibility Attribution"
) +
coord_flip() +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
legend.position = "none"
)


```

Mediation Analysis Plots

```{r}

library(dplyr)
library(ggplot2)

# mediation effects
med_effects <- data.frame(
  Effect = c("Indirect (ACME)", "Direct (ADE)", "Total Effect"),
  Estimate = c(med_out$d0, med_out$z0, med_out$tau.coef),
  Lower = c(med_out$d0.ci[1], med_out$z0.ci[1], med_out$tau.ci[1]),
  Upper = c(med_out$d0.ci[2], med_out$z0.ci[2], med_out$tau.ci[2])
)

# Plot
ggplot(med_effects, aes(x = Effect, y = Estimate)) +
  geom_point(size = 3, color = "steelblue") +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  labs(
    x = "",
    y = "Effect Estimate",
    title = "Mediation Analysis: Direct, Indirect, and Total Effects"
  ) +
  theme_minimal()
#reformatting
library(ggplot2)

# Adjusted mediation effects plot

ggplot(med_effects, aes(x = Effect, y = Estimate)) +
geom_point(size = 4, color = "#4FB663") +
geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2, size = 0.8, color = "#4FB663") +
geom_hline(yintercept = 0, linetype = "dashed", color = "#7f7f7f") +
coord_flip() +
labs(
x = "",
y = "Effect Estimate",
title = "Mediation Analysis: Direct, Indirect, and Total Effects"
) +
theme_minimal(base_family = "Helvetica") +
theme(
plot.background = element_rect(fill = "#ffffff", color = NA),
panel.background = element_rect(fill = "#DEDFDF", color = NA),
panel.grid.major = element_line(color = "#ffffff"),
panel.grid.minor = element_blank(),
axis.text = element_text(size = 12, color = "#333333"),
axis.title = element_text(size = 14, face = "bold"),
plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
legend.position = "none"
)


```

Mediation diagram

```{r}

library(ggplot2)
library(ggforce)

ggpredict(m2, terms = "resp_binary")
```

```{r}

# Descriptive Statistics
install.packages("skimr")
library(skimr)

vars <- c("resp_binary", "cons_media_type", "F_IDEO_w80", "F_GENDER_w80", "F_AGECAT_w80", "F_EDUCCAT2_w80", "F_INC_SDT1_w80", "JAN6HEARD_W80", "F_PARTYSUM_FINAL_w80")
skim_out <- skim(atp_rep_3[vars])

# Create HTML table
html_table <- kable(skim_out, format = "html") %>%
  kable_styling()

# Save to HTML file
save_kable(html_table, "skim_descriptives.html")

desc <- describe(atp_rep_3[vars])

# Convert describe() output to HTML manually
html <- paste0(
  "<html><body><h2>Descriptive Statistics</h2>",
  "<table border='1' cellpadding='5'>",
  "<tr><th>", paste(colnames(desc), collapse="</th><th>"), "</th></tr>",
  paste(
    apply(desc, 1, function(row)
      paste0("<tr><td>", paste(row, collapse="</td><td>"), "</td></tr>")
    ),
    collapse=""
  ),
  "</table></body></html>"
)

writeLines(html, "descriptive_stats.html")
#--

unique(atp_rep_3$F_PARTYSUM_FINAL_w80)

summary(med_out)

```
